Scheduling and Amortization for MPC

### 2022-02-02 biometric_vectorization_example.tex
Fixed typos in code.

In the code below, all initializations (e.g., \texttt{min\_sum!3 = i}), operations, and PHI nodes are \emph{implicitly vectorized}. 
$\mathit{raise\_dim}$ and $\mathit{drop\_dim}$ statements, as well as propagation statements (e.g., \texttt{min\_sum!3 = sum!3\^}) 
may have slightly different interpretation. \ana{This is vague but I think it's clear.}

@@

Starting at the inner phi-node \texttt{sum!3 = PHI(sum!2\^, sum!4)}, the algorithm first computes its closure. The closure amounts to the phi-node itself and the addition node \texttt{sum!4 = (sum!3 + p!3)}, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The dependences are from \texttt{p!3[I,J] = (d!3[I,J] * d!3[I,J])} to the monolithic FOR loop and from the FOR loop to \texttt{sum!3\^ = drop\_dim(sum!3)}. (Lower case index, e.g., $i,j$ indicates non-vectorized dimension, while uppercase index, e.g., $I$ indicates vectorized dimenion.)

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
   min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = [0,1,2,...,N!0-1]
   min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
\end{verbatim}
}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0))

@@

sum!3^ = drop_dim(sum!3)     
min_index!3 = [1,2,...N!0]   
min_sum!3 = sum!3^

>>>>

In the code below, all initializations (e.g., \texttt{min\_sum!3 = i}), operations, and PHI nodes are \emph{implicitly vectorized}. 
$\mathit{raise\_dim}$ and $\mathit{drop\_dim}$ statements, as well as propagation statements (e.g., \texttt{min\_sum!3 = sum!3\^}) 
may have slightly different interpretation. \ana{This is vague, may need elaboration.}

@@

Starting at the inner phi-node \texttt{sum!3 = PHI(sum!2\^, sum!4)}, the algorithm first computes its closure. The closure amounts to the phi-node itself and the addition node \texttt{sum!4 = (sum!3 + p!3)}, accounting for the loop-carried dependency of the computation of \texttt{sum}. The algorithm replaces this closure with a FOR loop on $j$ removing vectoriaztion on $j$. Note that the SUB and MUL computations remain outside of the loop as they do not depend on phi-nodes that are part of cycles. The dependences are from \texttt{p!3[I,J] = (d!3[I,J] * d!3[I,J])} to the monolithic FOR loop and from the FOR loop to \texttt{sum!3\^ = drop\_dim(sum!3)}. (Lower case index, e.g., \texttt{i}, indicates non-vectorized dimension, while uppercase index, e.g., \texttt{I} indicates vectorized dimension.)

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
  min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = [0,1,2,...,N!0-1]
  min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
\end{verbatim}
}

@@

@@

sum!3^ = drop_dim(sum!3)     
min_index!3 = [0,1,2,...N!0-1]   
min_sum!3 = sum!3^
